---
title: "TNUM"
author: "Maggie Sha"
date: "2020/11/19"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tnum)
library(tidyverse)
library(dplyr)
library(ggplot2)

devtools::install_github("truenumbers/tnum/tnum")
tnum.authorize(ip="54.158.136.133")
```


# Data cleaning and organization
```{r}
# "love" in sense and sensibility
num2 <- tnum.query("*sense* has text = REGEXP(\"love\")",max=200)
textdf <- tnum.objectsToDf(num2)
# View(textdf)

# str_split(tnum.getAttrFromList(num2[5], "subject"), "[:/]")

# returns chapter number
# as.numeric(substring(str_split(tnum.getAttrFromList(num2[5], "subject"), "[:/]")[[1]][4], 9))

# apply it in a loop
for(i in 1:length(num2)){
  textdf$chap_num[i] <- as.numeric(substring(str_split(tnum.getAttrFromList(num2[i], "subject"), "[:/]")[[1]][4], 9))
}
count1 <- textdf %>%  group_by(chap_num) %>% summarise(count = n())
```

##  Plots
```{r}
# bar chart
ggplot(count1,aes(x=chap_num,y=count)) + 
  geom_bar(stat="identity",fill="cadetblue3") +
  theme(axis.text.x=element_text(angle=90,hjust=1,vjust=0.5)) +
  geom_smooth(se=F) +
  ggtitle("counts of 'love' in each chapter of the book 'sense and sensibility'")
```

Explanation: from the plot above, the distribution of the word 'love' in 'sense and sensibility' follows a 'W' shape.
             In the early chapter 3 and final chapters 44, 45 and 49, this word is mentioned a lot more than the middle chapters.

             
             In the beginning of the book, the two daughters Elinor and Marianne in the Dashwood family lead a rich and peaceful life.
             They both have romantic relationships at that time, so the word 'love' is talked frequently.
             Edward Ferrars is Elinor's lover, he is a well-educated men from a rich family.
             However, after Dashwood passed away, all his money was passed to his first son, and the daughters left with a small income.
             Edward's mother does not support his relationship with Elinor, but Edward insisted. As a result,
             Edward is driven out of home and he gets no financial support from his family since then.
             Thus, in the middle plot, both of the characters are poor and they spend most of their time working and supporting themselves.
             This could be a possible reason that why 'love' is mentioned less frequently.
             Until in the end, their life become stable so they start to talk about 'love' again.

